### 2021-08-10 paper/paper.tex
Rewrite first paragraph of section 3

FLUXO\footnote{\url{https://github.com/project-fluxo/fluxo}} is an open source
MPI Fortran code implementing discontinuous Galerkin methods on unstructured hex
meshes in three space dimensions for advection-diffusion equations. It also
implements the same kind of modern, flux differencing DG methods
to achieve entropy conservation/dissipation or kinetic energy preservation.
At the same time, both codes have features the other does not, \eg,
approximation capabilities for parabolic equations and MPI in FLUXO
or multiple mesh types and more physics setups in \trixi. Nevertheless,
both \trixi and FLUXO share a common set of features, \eg, high-order DG
methods on 3D curvilinear meshes, that enables a reasonable comparison of their performance.

@@

Here, we compare the serial performance of \trixi and FLUXO when solving a
hyperbolic PDE in three space dimensions on curvilinear hex meshes.

>>>>

FLUXO\footnote{\url{https://github.com/project-fluxo/fluxo}} is an open source
Fortran code implementing discontinuous Galerkin methods on unstructured hexahedral
meshes in 3D for advection-diffusion equations. It provides
the same kind of modern, flux differencing DG methods
to achieve entropy conservation/dissipation or kinetic energy preservation that are used in \trixi.
At the same time, both codes have features the other does not, \eg,
support for parabolic equations and multi-node parallelism in FLUXO,
or multiple mesh types and more physics setups in \trixi. Nevertheless,
both \trixi and FLUXO share a common set of features, \ie, high-order DG
methods on 3D curvilinear meshes, which allows a reasonable comparison of their performance.

@@

Here, we compare the serial performance of \trixi and FLUXO when solving a
hyperbolic PDE in three space dimensions on curvilinear hexahedral meshes.
